---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# **sc**: simplicial complexes encoded as bipartite graphs

**sc** is a convenience package for encoding simplicial complexes in R as bipartite graphs using the **igraph** package. It is intended for temporary use, until superior functionality and perforance are achieved by other medium-level packages, for example an R interface to [the GUDHI C++ library](http://gudhi.gforge.inria.fr/) --- or until i become aware of them!

## Installation

Install the package from GitHub using [the **remotes** package](https://github.com/r-lib/remotes):

``` r
remotes::install_github("corybrunson/sc")
```

## Example

A popular illustration from Wikimedia Commons provides an illustration:

```{r example}
library(sc)
# load data
data(wiki_sc)
# inspection and visualization
print(wiki_sc)
plot(wiki_sc, vertex.label = NA)
# vertices and simplices
vertices(wiki_sc)
simplices(wiki_sc)
```
